Metagenomic Barcoding of Pollen Loads Offers Insights on the Foraging

### 2022-12-20 script/manuscript_MEE.Rmd
skeletor on a halfpipe in the discussion

We have demonstrated how hyb-seq data may be used in for plant barcoding in a metagenomic context.

@@

**Spatial ... & Timing ** (filters!)
- Fewer modelling runs for SDM's likely to be effective for determining inclusion, elastic inclusion criteria.
- The actual dataset which was used for training and testing all of the models incorporated into SDM's represented only roughly one quarter of the records available for such purposes. We consciously chose to do this in order to showcase the possibility of this approach working in less data rich areas. 
- Used fine scale flora to evaluate results of modelling, similar approaches based on quick field surveys which do not require comprehensive floristic endeavors.
- Timing in other areas may suffer complications due to lacking as strong a signal as that induced by snowmelt, but longer durations of flowering likely to help. 
- Sample size in phenology estimates had an effect which is likely to be maintained across all results.
- Regardless both show good agreement on flower onset, peak flowering, and moderate agreement with flowering cessation. The disagreement in flowering cessation is perhaps due to more microclimates which retain water, rather than microclimates which allow the early accumulation of heat. 
- Number of botanists rapidy decreasing and little hope for much more field based information

**Molecular ... **
- PAFTOL project provide complete genus level reference dataset for the kingdom
- Expected to work nearly immediately for dna barcoding of whole plant material.
- With work expected to work well in meta contexts. 
- Harvest both variable loci, and variable flanking regions of loci for fine taxonomic resolution
- Potential for infraspecific inference (@wenzell2021incomplete, Loke et al. in prep, Matt JOhnson has a paper on this too.)

**Final P**
 < bayesian framework >

In regards to better understanding the foraging preferences of *Bombus* feeding in subalpine ecosystems. **JANE AND PAUL SET UP FOR NEAR FUTURE RESULTS?**

>>>>

**overall stuff and things**
We have demonstrated how a533 data may be used for plant barcoding in a metagenomic context. This was exemplified in an ecologically realistic situation, centered both in a context which serves as an immediate framework for land management studies,  and which produced fundamental natural history information. These datasets included taxonomically difficult clades (e.g. Mertensia, Lupinus) .

@@

**Spatial ... & Timing ** (filters!)
- Fewer modelling runs for SDM's likely to be effective for determining inclusion, elastic inclusion criteria.
- The actual dataset which was used for training and testing all of the models incorporated into SDM's represented only roughly one quarter of the records available for such purposes. We consciously chose to do this in order to showcase the possibility of this approach working in less data rich areas. 
- Used fine scale flora to evaluate results of modelling, similar approaches based on quick field surveys which do not require comprehensive floristic endeavors.
- Timing in other areas may suffer complications due to lacking as strong a signal as that induced by snowmelt, but longer durations of flowering likely to help. 
- Sample size in phenology estimates had an effect which is likely to be maintained across all results.
- Regardless both show good agreement on flower onset, peak flowering, and moderate agreement with flowering cessation. The disagreement in flowering cessation is perhaps due to more microclimates which retain water, rather than microclimates which allow the early accumulation of heat. 
- Number of botanists rapidly decreasing no hope for much more field based information or funding.

**Molecular ... **
- PAFTOL project provide complete genus level reference dataset for the kingdom
- Expected to work nearly immediately for DNA barcoding of whole plant material.
- With work expected to work well in meta contexts. 
- Harvest both variable loci, and variable flanking regions of loci for fine taxonomic resolution
- Potential for infra-specific inference (@wenzell2021incomplete, Loke et al.,  @slimp2021potential, @beck2021palmer).

**Final P**
 < bayesian framework > < harvesting loci >
